---
title: "ten-step-workflow"
author: "Onkar Singh"
date: "11/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xaringan)
library(usethis)
```

[Ten Step Workflow](https://rviews.rstudio.com/2021/11/18/deploying-xaringan-slides-a-ten-step-github-pages-workflow/#initialize-version-control-with-git)

2.  Create a xaringan deck using a xaringan template:

File \> New File \> R Markdown \> From Template \> Ninja Presentation \> OK

3.  Delete what you don't need and save your R Markdown file with whatever name you like. If you pick index.Rmd the live link you share at the end will be relatively short.

4.  

    4.  Render HTML slides from the open Rmd file using xaringan's infinite moon reader:

xaringan::infinite_moon_reader()

## Deploying your slides

**9. When you're ready to deploy your slides, you can use the `usethis::use_github_pages()` function** which makes the process of deploying via GitHub Pages super easy. I recommend pointing `branch` to the name of your primary branch.

    usethis::use_github_pages(branch = "master") # use main in place of master

> Note: Your repository must be **public** for your deployed slides to be available publicly, unless you have a paid GitHub account.

\

> Also, you only need to follow this step *once* to deploy your slides to the web. As long as you remember to push to your repo any changes that you make to your slides (Rmd and HTML), GitHub Pages will know how to render them.

**10. Visit the link provided to see your newly deployed slides!** 🚀\
Don't panic if you don't see them right away, sometimes it takes a little time. This is the link you will share with the world when you present. Notice it looks *very* similar to your GitHub repo link.\

> Link to the R-Ladies xaringan template rendered slides:\
> <https://spcanelon.github.io/RLadies-xaringan-template>

# Bonus steps

11\. Go to the [repository home page](https://github.com/spcanelon/RLadies-xaringan-template) and find the About section on the right hand side. Add a description of your presentation and the link to your slides, that way your presentation is easily available to anyone visiting your repo.

12\. Check out Garrick Aden-Buie's blog post Sharing Your xaringan Slides to learn how to [create a social media card](https://www.garrickadenbuie.com/blog/sharing-xaringan-slides/#create-a-social-media-card) for your slides and use your new link to share your slides in more places (e.g. [embedded on a website](https://www.garrickadenbuie.com/blog/sharing-xaringan-slides/#embed-your-slides), etc.)

13\. This GitHub Pages workflow is not exclusive to xaringan slides! Try it out with any other HTML file.

# Learn more

## Foundation

-   [Sharing Your Work with xaringan • Silvia Canelón](https://spcanelon.github.io/xaringan-basics-and-beyond/index.html) -- workshop site

-   [Introducción al Paquete xaringan • Silvia Canelón](https://silvia.rbind.io/talk/2020-12-17-introduccion-xaringan/) -- R-Ladies Meetup

-   [Making Slides with R Markdown • Alison Hill](https://arm.rbind.io/slides/xaringan.html) -- workshop slides

-   [Presentation Ninja • xaringan Official Document](https://slides.yihui.org/xaringan/) -- package documentation

-   [Chapter 7 xaringan Presentations • R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/xaringan.html) -- book chapter

## Sharing your slides

-   [Sharing Your xaringan Slides • Garrick Aden‑Buie](https://www.garrickadenbuie.com/blog/sharing-xaringan-slides/) -- blog post

-   [Functions For Building Xaringan Slides To Different Outputs. • xaringanBuilder](https://jhelvy.github.io/xaringanBuilder/) -- package site

-   [Sharing on Short Notice • Alison Hill & Desirée De Leon](https://alison.rbind.io/talk/2020-sharing-short-notice/) -- video resource for deploying via Netlify

## Making your slides extra special

-   [Professional, Polished, Presentable • Garrick Aden‑Buie & Silvia Canelón • useR!2021](https://presentable-user2021.netlify.app/) -- workshop site

-   [Home · yihui/xaringan Wiki • GitHub](https://github.com/yihui/xaringan/wiki) -- wiki of customizations for xaringan

-   [Making Extra Great Slides • Garrick Aden‑Buie](https://www.garrickadenbuie.com/talk/extra-great-slides-nyhackr/) -- talk & slides with xaringan overview and featuring CSS styling and xaringanthemer

-   [Applying design guidelines to slides with {xaringanthemer} • katie jolly](https://www.katiejolly.io/blog/2021-03-16/designing-slides) -- blog post

-   [A playground of extensions for xaringan • xaringanExtra](https://pkg.garrickadenbuie.com/xaringanExtra/#/?id=xaringanextra) -- package site

-   [Custom xaringan CSS Themes • xaringanthemer](https://pkg.garrickadenbuie.com/xaringanthemer/) -- package site

*Note from the Editor: Silvia's post is a mini masterpiece of clear, concise writing that elucidates complex technology within the narrow context of explaining a single well-defined task. Silvia does not attempt to say everything she knows about the subject, and she resists digressions that might obscure the path she is laying out. It is an example of achieving clarity through saying less.*
